\subsection{Palladium \href{https://www.palladiummag.com/}{\ding{225}}}
\subsubsection{Walter Kirn on How America Lost the Plot \href{https://www.palladiummag.com/2023/07/25/walter-kirn-on-how-america-lost-the-plot/}{\ding{225}}}
\textit{25-Jul-2023}

The novelist turns his literary eye to the American story and finds we're losing our memories under a new imperative to forget.
The post <a href="https://www.palladiummag.com/2023/07/25/walter-kirn-on-how-america-lost-the-plot/">Walter Kirn on How America Lost the Plot
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{Don’t Learn Value From Society \href{https://www.palladiummag.com/2023/07/13/dont-learn-your-values-from-society/}{\ding{225}}}
\textit{14-Jul-2023}

We face a crisis of false value. Ancient perspectives like that of Abraham offer a way out.
The post <a href="https://www.palladiummag.com/2023/07/13/dont-learn-your-values-from-society/">Don’t Learn Value From Society
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{The Triumph of the Good Samaritan \href{https://www.palladiummag.com/2023/07/06/the-triumph-of-the-good-samaritan/}{\ding{225}}}
\textit{07-Jul-2023}

Those trying to justify parasitic behaviors often invoke the language of charity and compassion. But true charity is about enforcing a superior form of life.
The post <a href="https://www.palladiummag.com/2023/07/06/the-triumph-of-the-good-samaritan/">The Triumph of the Good Samaritan
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{When Every Child Is a Choice \href{https://www.palladiummag.com/2023/06/29/when-every-child-is-a-choice/}{\ding{225}}}
\textit{29-Jun-2023}

As a normal life becomes more difficult for middle class parents to acquire, optimizing a child's upbringing for educational and career success has become the norm—but at great expense. Is there another way?
The post <a href="https://www.palladiummag.com/2023/06/29/when-every-child-is-a-choice/">When Every Child Is a Choice
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{The Answer Is Better Gangs \href{https://www.palladiummag.com/2023/06/22/the-answer-is-better-gangs/}{\ding{225}}}
\textit{22-Jun-2023}

As long as criminal enterprises offer the best gangs around, kids will continue to enter them. The question is where the better gangs could be.
The post <a href="https://www.palladiummag.com/2023/06/22/the-answer-is-better-gangs/">The Answer Is Better Gangs
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{Why I Live in San Francisco \href{https://www.palladiummag.com/2023/06/13/why-i-live-in-san-francisco/}{\ding{225}}}
\textit{13-Jun-2023}

San Francisco is upstream of America, and its social crises are spilling across the country. It is also the best place to find a path out.
The post <a href="https://www.palladiummag.com/2023/06/13/why-i-live-in-san-francisco/">Why I Live in San Francisco
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{PALLADIUM 10: Cultural Excellence \href{https://www.palladiummag.com/2023/06/07/palladium-10-cultural-excellence/}{\ding{225}}}
\textit{07-Jun-2023}

Master your craft. Excellence is timeless. PALLADIUM 10: Cultural Excellence, our summer print edition, is now available, featuring exclusive interviews and custom artwork.
The post <a href="https://www.palladiummag.com/2023/06/07/palladium-10-cultural-excellence/"><b><b>PALLADIUM</b> 10:</b> Cultural Excellence
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{“At the Edge of Life” With Pietro Boselli \href{https://www.palladiummag.com/2023/06/07/at-the-edge-of-life-with-pietro-boselli/}{\ding{225}}}
\textit{07-Jun-2023}

Pietro Boselli is a model, mechanical engineer, and adventurer. He discusses the value of many sources of experience, trusting your instincts, and death-defying solo trips into the unknown.
The post <a href="https://www.palladiummag.com/2023/06/07/at-the-edge-of-life-with-pietro-boselli/"><i>“At the Edge of Life”</i> With Pietro Boselli
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{School Is Not Enough \href{https://www.palladiummag.com/2023/06/06/school-is-not-enough/}{\ding{225}}}
\textit{06-Jun-2023}

Children need purposeful work to develop agency and self-possession. That education is unlikely to happen in school.
The post <a href="https://www.palladiummag.com/2023/06/06/school-is-not-enough/">School Is Not Enough
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{Complex Systems Won’t Survive the Competence Crisis \href{https://www.palladiummag.com/2023/06/01/complex-systems-wont-survive-the-competence-crisis/}{\ding{225}}}
\textit{01-Jun-2023}

Complex systems like air traffic and energy operate on rigorous competency. With the managers of these systems prioritizing goals like diversity, these networks are now eroding.
The post <a href="https://www.palladiummag.com/2023/06/01/complex-systems-wont-survive-the-competence-crisis/">Complex Systems Won’t Survive the Competence Crisis
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{Industrial Civilization Needs a Biological Future \href{https://www.palladiummag.com/2023/05/18/industrial-civilization-needs-a-biological-future/}{\ding{225}}}
\textit{19-May-2023}

The core "WEIRD" populations of industrial society are getting consumed by it. They need to biologically assert themselves for technological civilization to survive.
The post <a href="https://www.palladiummag.com/2023/05/18/industrial-civilization-needs-a-biological-future/">Industrial Civilization Needs a Biological Future
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{ESG Is the Opium of the Investors \href{https://www.palladiummag.com/2023/05/05/esg-is-the-opium-of-the-investors/}{\ding{225}}}
\textit{05-May-2023}

ESG has created a luxury good out of symbolic pro-social investing. In practice, it mainly replicates consensus ideology. Those who want to go beyond it must act directly on the world.
The post <a href="https://www.palladiummag.com/2023/05/05/esg-is-the-opium-of-the-investors/"><b>ESG</b> Is the Opium of the Investors
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{Britain Is Dead \href{https://www.palladiummag.com/2023/04/27/britain-is-dead/}{\ding{225}}}
\textit{28-Apr-2023}

Despite its early industrial dominance, Britain's elites never managed to adapt to the new landscape of power. After more than a century of structural breakdown, its very future as a unified state is in doubt.
The post <a href="https://www.palladiummag.com/2023/04/27/britain-is-dead/">Britain Is Dead
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{Entrepreneurial Statecraft Gets the Goods \href{https://www.palladiummag.com/2023/04/25/entrepreneurial-statecraft-gets-the-goods/}{\ding{225}}}
\textit{26-Apr-2023}

You don't reshape society by starting a cultural movement. Instead, you need to implement direct action materialism.
The post <a href="https://www.palladiummag.com/2023/04/25/entrepreneurial-statecraft-gets-the-goods/">Entrepreneurial Statecraft Gets the Goods
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{Who Is the Art World For? \href{https://www.palladiummag.com/2023/04/20/who-is-the-art-world-for/}{\ding{225}}}
\textit{20-Apr-2023}

Art today often aims to shock rather than inspire. How did that change happen?
The post <a href="https://www.palladiummag.com/2023/04/20/who-is-the-art-world-for/">Who Is the Art World For?
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{The Smallest Living Things, A Short Film \href{https://www.palladiummag.com/2023/04/17/smallest-living-things-a-film/}{\ding{225}}}
\textit{17-Apr-2023}

The health of the smallest living things is necessary for the survival of all life on Earth. This short film, directed by Charles Abelmann, tells the story of one self-made farmer’s quest to care for microbiomes—and call out the abuse of antibiotic overuse in livestock and people.
The post <a href="https://www.palladiummag.com/2023/04/17/smallest-living-things-a-film/">The Smallest Living Things, A Short Film
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{“A Pride in the Craft” With Bill Bensley \href{https://www.palladiummag.com/2023/04/13/a-pride-in-the-craft-with-bill-bensley/}{\ding{225}}}
\textit{13-Apr-2023}

Bill Bensley looks back on decades of perfecting his maximalist design philosophy in Asia. He discusses his approach to cultural interpretation, ecological synthesis, and the pursuit of artistic excellence.
The post <a href="https://www.palladiummag.com/2023/04/13/a-pride-in-the-craft-with-bill-bensley/"><i>“A Pride in the Craft”</i> With Bill Bensley
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
\subsubsection{Journey to the Golden Age \href{https://www.palladiummag.com/2023/04/11/journey-to-the-golden-age/}{\ding{225}}}
\textit{12-Apr-2023}

Golden ages leave behind the undying fame of their heroes. It is those who engage them as peers that become capable of initiating a new one.
The post <a href="https://www.palladiummag.com/2023/04/11/journey-to-the-golden-age/">Journey to the Golden Age
 appeared first on <a href="https://www.palladiummag.com/">Palladium.
